NSHRDLU?

### 2015-10-22 writing/gist/model1_fig.tex
Writing: Buffer size change.

    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{tracker}=[fill=red!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{softmax}=[fill=blue!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{result}=[line width=1pt,draw=black,text width=15mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=10mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=5.5mm]

@@

    \node[focus2] (0sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (0s1) at (\ox+0*\dx,\sy-1*\dy) {cat};
    \node[word]  (0s2) at (\ox+0*\dx,\sy+0*\dy) {the};
    \node[word]  (0s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (0sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \node[focus2] (1sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (1s1) at (\ox+0*\dx,\sy-1*\dy) {the cat};
    \node[word]  (1s2) at (\ox+0*\dx,\sy+0*\dy) {};
    \node[word]  (1s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (1sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \node[focus2] (2sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (2s1) at (\ox+0*\dx,\sy-1*\dy) {sat};
    \node[word]  (2s2) at (\ox+0*\dx,\sy+0*\dy) {the cat};
    \node[word]  (2s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (2sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{tracker}=[fill=red!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{softmax}=[fill=orange!40,text width=33mm,align=center,text height=2mm]
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{result}=[line width=1pt,draw=black,text width=15mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=33mm,align=center,text height=10mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=33mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=33mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=33mm,align=center,text height=5.5mm]

@@

    \node[focus2] (1sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (1s1) at (\ox+0*\dx,\sy-1*\dy) {cat};
    \node[word]  (1s2) at (\ox+0*\dx,\sy+0*\dy) {the};
    \node[word]  (1s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (1sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \node[focus2] (2sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (2s1) at (\ox+0*\dx,\sy-1*\dy) {the cat};
    \node[word]  (2s2) at (\ox+0*\dx,\sy+0*\dy) {};
    \node[word]  (2s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (2sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \node[focus2] (3sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (3s1) at (\ox+0*\dx,\sy-1*\dy) {sat};
    \node[word]  (3s2) at (\ox+0*\dx,\sy+0*\dy) {the cat};
    \node[word]  (3s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (3sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \node[focus2] (4sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (4s1) at (\ox+0*\dx,\sy-1*\dy) {down};
    \node[word]  (4s2) at (\ox+0*\dx,\sy+0*\dy) {sat};
    \node[word]  (4s3) at (\ox+0*\dx,\sy+1*\dy) {the cat};
    \node[sbox] (4sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \node[focus2] (5sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (5s1) at (\ox+0*\dx,\sy-1*\dy) {sat down};
    \node[word]  (5s2) at (\ox+0*\dx,\sy+0*\dy) {the cat};
    \node[word]  (5s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (5sb) at  (\ox+0*\dx,\sy+0*\dy) {};

@@

    \node[focus2] (6sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (6s1) at (\ox+0*\dx,\sy-1*\dy) {(the cat) (sat down)};
    \node[word]  (6s2) at (\ox+0*\dx,\sy+0*\dy) {};
    \node[word]  (6s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (6sb) at  (\ox+0*\dx,\sy+0*\dy) {};

>>>>

    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{tracker}=[fill=red!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{softmax}=[fill=blue!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{result}=[line width=1pt,draw=black,text width=15mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=13.3mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=25mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=25mm,align=center,text height=5.5mm]

@@

    \node[focus2] (0sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (0s1) at (\ox+0*\dx,\sy-1*\dy) {cat};
    \node[word]  (0s2) at (\ox+0*\dx,\sy+0*\dy) {the};
    \node[word]  (0s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (0sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \node[focus2] (1sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (1s1) at (\ox+0*\dx,\sy-1*\dy) {the cat};
    \node[word]  (1s2) at (\ox+0*\dx,\sy+0*\dy) {};
    \node[word]  (1s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (1sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \node[focus2] (2sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (2s1) at (\ox+0*\dx,\sy-1*\dy) {sat};
    \node[word]  (2s2) at (\ox+0*\dx,\sy+0*\dy) {the cat};
    \node[word]  (2s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (2sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \tikzstyle{word}=[text width=35mm,align=center,text height=2mm]    
    \tikzstyle{tracker}=[fill=red!40,text width=15mm,align=center,text height=2mm]
    \tikzstyle{softmax}=[fill=orange!40,text width=33mm,align=center,text height=2mm]
    \tikzstyle{comp}=[fill=green!40,text width=20mm,align=center,text height=2mm]
    \tikzstyle{result}=[line width=1pt,draw=black,text width=15mm,align=center,text height=2mm]    
    \tikzstyle{sbox}=[line width=1pt,draw=black,text width=33mm,align=center,text height=13.3mm]
    \tikzstyle{bbox}=[line width=1pt,draw=black,text width=33mm,align=center,text height=6.5mm]
    \tikzstyle{focus1}=[fill=yellow!80,opacity=0.5,text width=33mm,align=center,text height=2mm]
    \tikzstyle{focus2}=[fill=yellow!80,opacity=0.5,text width=33mm,align=center,text height=5.5mm]

@@

    \node[focus2] (1sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (1s1) at (\ox+0*\dx,\sy-1*\dy) {cat};
    \node[word]  (1s2) at (\ox+0*\dx,\sy+0*\dy) {the};
    \node[word]  (1s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (1sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \node[focus2] (2sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (2s1) at (\ox+0*\dx,\sy-1*\dy) {the cat};
    \node[word]  (2s2) at (\ox+0*\dx,\sy+0*\dy) {};
    \node[word]  (2s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (2sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \node[focus2] (3sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (3s1) at (\ox+0*\dx,\sy-1*\dy) {sat};
    \node[word]  (3s2) at (\ox+0*\dx,\sy+0*\dy) {the cat};
    \node[word]  (3s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (3sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \node[focus2] (4sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (4s1) at (\ox+0*\dx,\sy-1*\dy) {down};
    \node[word]  (4s2) at (\ox+0*\dx,\sy+0*\dy) {sat};
    \node[word]  (4s3) at (\ox+0*\dx,\sy+1*\dy) {the cat};
    \node[sbox] (4sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \node[focus2] (5sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (5s1) at (\ox+0*\dx,\sy-1*\dy) {sat down};
    \node[word]  (5s2) at (\ox+0*\dx,\sy+0*\dy) {the cat};
    \node[word]  (5s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (5sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};

@@

    \node[focus2] (6sb) at  (\ox+0*\dx,\sy-0.5*\dy) {};
    \node[word]  (6s1) at (\ox+0*\dx,\sy-1*\dy) {(the cat) (sat down)};
    \node[word]  (6s2) at (\ox+0*\dx,\sy+0*\dy) {};
    \node[word]  (6s3) at (\ox+0*\dx,\sy+1*\dy) {};
    \node[sbox] (6sb) at  (\ox+0*\dx,\sy+0.5*\dy) {};
